Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2021-01-24 manuscript/response_to_reviews.Rmd

Re: "Carbon cycling in mature and regrowth forests globally" by Anderson-Teixeira, Kristina; Herrmann, Valentine; Banbury Morgan , Rebecca ; Bond-Lamberty, Benjamin; Cook-Patton, Susan; Ferson , Abigail; Muller-Landau, Helene; Wang, Maria
Article reference: ERL-109898

## LETTER TO EDITOR:

The most substantive changes included the following:

- Changed the figure set in accordance with comments from R3. Specifically, we
(1) added a schematic figure, somewhat in the style of @odum_strategy_1969, to help with conceptual framing of the review
(2) added a figure synthesizing changes in fluxes through time for each biome;
(3) removed maps from age trend diagrams (maps still available in SI), which makes the figures less busy/ easier to read; and
(4) moved C cycle diagrams for young forests to SI;

@@

Finally, I wondered about the interacting effects of changing climate (rising CO2, warming temperatures) and stand age, especially in determining trends in the pools. Mature forests will have experienced a much wider range of climate conditions than younger stands. How does this complicate the comparison of live biomass across forest of different age?

**This is an excellent question, and one that is of great interest to the lead author [e.g., @andersonteixeira_altered_2013]; however, we think it is unlikely to have much influence at this relatively coarse scale of analysis, especially given that much of the data in ForC was collected in the 20th century. Sorting this out would require carefully designed studies, and probably would not be possible using ForC data at this point.**

Second, I had some questions about the representativeness of the dataset. While I appreciate that the authors choose to use distinct geographic areas as the unit of analysis (avoiding some issues of pseudo-replication from many observations from a single site), I still wondered about the extent to which the distinct geographic areas were representative of the climate space within each biome. For example, if mean annual climate versus presentation for all boreal, temperate and tropical locations are shown in a scatterplot (for example, using reanalysis data), and then mean annual temperature and precipation of the observations are shown on top, how much of the “climate space” is covered by the dataset?

**An analysis of this type would need to be fairly involved, including a separate analysis for each variable. While do-able (we have previously published a plot similar to that described for the entire database), such an analysis would only begin to cover important aspects of representativeness (MAT and MAP, but not seasonality, soils, floristic composition, etc.). We feel that, in this case, the insights gained from the analysis would not justify the strain on time and resources that it would require. We have, however, given additional attention to the issue of representativeness in the revision. Specifically, we have done the following:**

- **Set the stage for discussion of within-biome variability by including error bars on our schematic figure (Fig. 1).**

- **Ensured that the issue is clearly and transparently presented in the figures--for example, by adding the following statement to the captions of Figures 3-6 (formerly 2-5): "Note that variables differ in geographical representation, resulting in potential imbalances (Figs. S5-S30). Probability that estimates reflect true biome means scales with the number of distinct geographical areas represented." **

- **Revisited our presentation of representativeness issues in the results and discussion, revising text to ensure clear communication of the concept that biomed differences were influenced by geographical representation within the biome. For example, our discussion of stock differences across biome differences now reads: "...For $B_{tot}$ and $B_{ag}$, tropical broadleaf forests had the highest mean biomass and boreal forests the lowest, with temperate broadleaf and needleleaf ($B_{ag}$ only) intermediate. However, maximum values for stocks including live or standing woody biomass ($B_{tot}$, $B_{ag}$, $B_{ag-wood}$, $B_{root}$, $B_{root_coarse}$, $DW_{tot}$, $DW_{standing}$) consistently occurred in temperate biomes (Figs. 1, 8, S20-S30). For variables that were disproportionately sampled in such high-biomass forests ($B_{ag-wood}$, $B_{foliage}$, and $B_{root-coarse}$; disproportionately sampled in  the US Pacific Northwest), temperate conifer forests had significantly higher stocks than the other biomes."**

@@

Third, I found the presentation of the results made it difficult to see clearly the major differences in C fluxes and pools across biomes and age classes. The illustrated C budgets (the majority of the figures, 8 in total) are visually very appealing, but the reader has to do a lot of flipping back and forth to see how any particular flux or pool varies across biomes and age class. Figure 6 is more synthetic, but each panel is very small and the differences from one group to the next are hard to see. It is also difficult to compare results for young forests (as scatterplots) with the box plots for the mature forests.  My advice is to move some of the budgets to SI, and include in the main manuscript more figures that clearly illustrate the most interesting trends with biome, and to allow an expansion of the results in Figure 6 (for example, by first showing scatterplots of all forests, young and old, as a function of stand age), and then perhaps another that is a box plot comparison of mature versus old forests in each biome.

**We have done a major re-arrangment of figures, including the following: (1) added a schematic figure, somewhat in the style of @odum_strategy_1969, to help with conceptual framing of the review; (2) added a figure synthesizing changes in fluxes through time for each biome; (3) removed maps from age trend diagrams (maps still available in SI), which makes the figures less busy/ easier to read; and (4) moved C cycle diagrams for young forests to SI. The result is that (1) the main manuscript contains only the more informative illustrated C budgets (mature forests); (2) the figures showing age trends and biome differences in 6 C flux and stock variables (Figs. 7-8, formerly 6-7) are much easier to read; and (3) the new figure 9 provides an overall synthesis of results, focusing on the most trusted variables.**

**Regarding the suggestion of showing age of old forests as a scatterplot, this is unfortunately not possible give unknown ages of most mature tropical forests, as explained above.**

@@

A few other comments:

Page 6, first paragraph: I wondered about the extent to which filtering the data for “managed” affected the results. In the Eastern US, for example, its difficult to find any forests on public land that aren’t managed to some extent (for example, through periodic selective harvests), and many of them regenerated from “planted” stands back in the 1930s. I would be curious to know if including “managed” forests substantially altered results.

The binary age classification (two ages, less than 100 years or greater than 100 years) was difficult to accept, as forests that are in the 80-100 year age range are often considered to be mature (at least in the temperate zone). I realize that even with a dataset as rich as For C, data availability will limit stratification into too many bins. Nonetheless, at least for some measurements, I wonder if it's possible to consider a greater number of age classes (for example, young, maturing, and mature).

**We prefer not to separate forests of known age into categories, but rather to represent age as a continuous variable, when possible. In large part this is motivated by the fact that appropriate age thresholds for various categories would vary across biomes, given differences in biomass accumulation rates. While our ideal would be to have no categorical divisions, unknown stand ages--particularly in the tropics--force us to divide the data into the categories used here.**

**To provide a better representation of age trends, we created new figure 9. Although it does not break forests into additional age categories, it does address what seems to be at the core of this concern, which is a concise representation of differences across the full range of stand ages.**

@@

The consistency check (e.g. do component fluxes/pools sum to within one standard deviation of the aggregate flux or pool) seems like it is destined to provide a favorable assessment of the degree of closure so long as the data within each grouping represent a wide range of natural climatic and soil variability. As long as the aggregate variable has a large standard deviation, the results are likely guaranteed to be “consistent.” It seems this metric would benefit from some simulations (perhaps with artificially generated data) to understand exactly how poor closure needs to be at the site-level to generate an inconsistent results when aggregated across sites.

**We agree that such an analysis would be valuable, but time and resource constraints place it beyond the scope of what is currently feasible in this already very large analysis. We believe that the current consistency check is valuable as a first pass for identifying cases of extreme mis-matches, and therefore retain it as is. However, we agree that it is not the ideal test, and that it is not very stringent (given high standard deviations) and have therefore toned down claims that the budgets are "closed"/"internally consistent" throughout the manuscript (e.g., removed from abstract). We note that the discussion already stated that our criteria for closure was relatively loose (and this statement is unchanged in the revised version): "On the other, however, *ForC* derives data from multiple heterogeneous sources, and standard deviations within each biome are high; as a result, the standard for C closure is relatively loose [*c.f.* @houghton_terrestrial_2020]."**

### 2021-01-24 manuscript/ERL_global_C_review.Rmd
finished responses to R3
I think this is good to go.... But see issue #57

*Methods/Design.* Here, we draw from the Global Forest Carbon Database, ForC, to provide a macroscopic overview of C cycling in the world’s forests, giving special attention to stand age-related variation. Specifically, we use `r n_records` *ForC* records for `r nrow(T1)` C cycle vaariables from `r n_areas_tot` geographic locations to characterize ensemble C budgets for four broad forest types -- tropical broadleaf evergreen, temperate broadleaf, temperate conifer, and taiga. We include estimates for both mature and regrowth (age <100 years) forests, and quantify trends with stand age in regrowth forests for all variables with sufficient data.

@@

```{r schematic, eval = generate_figures, echo=FALSE, fig.align = "center", fig.cap = "Figure 1 | Schematic diagram summarizing current understanding of biome differences and age trends in forest C cycling. Variables are defined in Table 1. Age trends, which represent idealized dynamics following a disturbance that removes all living vegetation, are an updated version of the classic figure from Odum (1969), with heavy lines corresponding to those in Odum's figure and $NEP$ corresponding to Odum's 'net production'. Here, $NEP$ conists primarily of woody aboveground net primary production ($ANPP_{woody}$), while $ANPP_{woody.turnover}$ is the sum of woody mortality and branch turnover. Dotted lines refer to decomposition of potential 'legacy' organic material produced prior to the disturbance and remaining at the site (e.g., standing and fallen dead wood, $DW_{tot}$).", out.width='100%', fig.pos='H'}

@@

Data were summarized to produce schematics of C cycling across the eight biome by age group combinations identified above.
To obtain the values reported in the C cycle schematics, we first averaged any repeated measurements within a plot.
Values were then averaged across geographically distinct areas, defined as plots clustered within 25 km of one another [*sensu* @anderson-teixeira_forc_2018], weighting by area sampled if available for all records.
This step was taken to avoid pseudo-replication.

@@

To test for age trends in young (<100yrs) forests, we employed a mixed effects model with biome and log10[stand.age] as fixed effects and plot nested within geographic.area as a random effect on the intercept.
This analysis was run for variables with records for at least three distinct geographic areas in more than one biome, excluding any biomes that failed this criteria (Table 1). 
When the effect of stand age was significant at p $\le$ 0.05 and when each biome had records for stands of at least 10 different ages, a biome $\times$ stand.age interaction was included in the model.

@@

For variables with records from $\ge$ 7 distinct geographic areas, these ensemble C budgets were generally consistent.
That is, component variables summed to within one standard deviation of their respective aggregate variables in all but one instance.
In the temperate conifer biome, the average composite measure of root biomass ($B_{root}$) was less than the combined average value of coarse and fine root biomass ($B_{root-coarse}$ and $B_{root-fine}$, respectively).
This lack of closure was driven by very high estimates of $B_{root-coarse}$ from high-biomass forests of the US Pacific Northwest.

@@

```{r eval = generate_figures, echo=FALSE, fig.align = "center", fig.cap = "Figure 7 | Age trends and biome differences in some of the major C fluxes: (a) $GPP$, (b) $NPP$, (c) $ANPP$, (d) $R_{soil}$, (e) $R_{eco}$, and (f) $NEP$. In each panel, the left scatterplot shows age trends in forests up to 100 years old, as characterized by a linear mixed effects model with fixed effects of age and biome. The fitted line indicates the effect of age on flux (solid lines: significant at p<0.05, dashed lines: non-significant), and non-parallel lines indicate a significant age x biome interaction. The boxplot illustrates distribution across mature forests, with different letters indicating significant differences between biomes. Data from biomes that did not meet the sample size criteria (see Methods) are plotted, but lack regression lines (young forests) or test of differences across biomes (mature forests). Individual figures for each flux with sufficient data are given in the Supplement (Figs. S4-S19).", out.width='100%', fig.pos='H'}

@@

There were sufficient data to assess mature forest biome differences for nine stock variables, and significant differences among biomes were detected for five variables ($B_{tot}$, $B_{ag}$, $B_{ag-wood}$, $B_{foliage}$, $B_{root-coarse}$; Table 1).
C stocks had less consistent patterns across biomes (Figs. `r stock_age_trends`, `r all_stock_age_trends`).
For $B_{tot}$ and $B_{ag}$, tropical broadleaf forests had the highest biomass and boreal forests the lowest, with temperate broadleaf and needleleaf ($B_{ag}$ only) intermediate.
For three variables that had been disproportionately sampled in the high-biomass forests of the US Pacific Northwest ($B_{ag-wood}$, $B_{foliage}$, and $B_{root-coarse}$), temperate conifer forests had significantly higher stocks than the other biomes, which were not significantly different from one another.

```{r eval = generate_figures, echo=FALSE, fig.align = "center", fig.cap = "Figure 8 | Age trends and biome differences in some of the major forest C stocks: (a) aboveground biomass, (b) foliage, (c) fine roots, (d) dead wood. In each panel, the left scatterplot  shows age trends in forests up to 100 years old, as characterized by a linear mixed effects model with fixed effects of age and biome. The fitted line indicates the effect of age on flux (solid lines: significant at p<0.05, dashed lines: non-significant), and non-parallel lines indicate a significant age x biome interaction. The boxplot illustrates distribution across mature forests, with different letters indicating signifant differences between biomes. Data from biomes that did not meet the sample size criteria (see Methods) are plotted, but lack regression lines (young forests) or test of differences across biomes (mature forests). Individual figures for each stock with sufficient data are given in the Supplement (Figs. S20-S30).", out.width='100%', fig.pos='H'}

@@

*ForC* v3.0 provided unprecedented coverage of most major variables, yielding a broad picture of C cycling in the world's major forest biomes.
Carbon cycling rates generally increased from boreal to tropical regions and with stand age.
Specifically, most C fluxes were highest in tropical forests, intermediate in temperate (broadleaf or conifer) forests, and lowest in boreal forests -- a pattern that generally held for regrowth as well as mature forests (Figs. `r flux_age_trends`- `r stock_age_trends`).
The notable exception was mature forest $NEP$, which, as the difference between $GPP$ and $R_{eco}$, was indistinguishable across biomes.
There was also little directional variation in mean mature forest C stocks across biomes, although maximum values for stocks including live or standing woody biomass ($B_{tot}$, $B_{ag}$, $B_{ag-wood}$, $B_{root}$, $B_{root_coarse}$, $DW_{tot}$, $DW_{standing}$) consistently occurred in temperate biomes (Figs. `r schematic`, `r `all_diagrams_mature`, `r stock_age_trends`).
Consistent with theory and previous studies (Fig. `r schematic`), the majority of flux variables, together with most live biomass pools, increased significantly with stand age (Table 1; Figs. `r flux_age_trends`- `r age_trends_all`, `r all_age_trends`).
Together, these results indicate that, moving from cold to tropical climates and from young to old stands, there is a general acceleration of C cycling, whereas C stocks and $NEP$ of mature forests, which are defined by the differences between in- and out- fluxes, do not vary systematically across biomes.
Together, these results refine and expand out understanding of C cycling in mature forests, while providing the first global-scale analysis of age trends in multiple forest C stocks and fluxes (Figs. `r age_trends_all`).

@@

In this analysis, the C cycle budgets for mature forests (Figs. `r all_diagrams_mature`) generally “close”–-that is, the sums of component variables do not differ from the larger fluxes by more than one standard deviation. 
On the one hand, this reflects the general fact that ecosystem-scale measurements tend to close the C budget more easily and consistently than, for example, for energy balance [@stoy_data-driven_2013]. 
On the other, however, *ForC* derives data from multiple heterogeneous sources, and standard deviations within each biome are high; as a result, the standard for C closure is relatively loose [*c.f.* @houghton_terrestrial_2020]. 
The one instance where the C budgets doesn’t close is likely due to differences in the representation of forest types (*i.e.*, disproportionate representation of US Pacific NW for  $B_{root-coarse}$ relative to  $B_{root}$; Fig. `r diagram_TeN_mature`) rather than issues of methodological accuracy. 
The overall high degree of closure implies that *ForC* gives a consistent picture of C cycling within biomes for mature forests. 
This is an important and useful test, because it allows for consistency checks within the C cycle, for example leveraging separate and independently-measured fluxes to constrain errors in another [@phillips_value_2017; @williams_impacts_2014; @harmon_heterotrophic_2011], or producing internally consistent global data products [@wang_golum-cnp_2018].

>>>>

*Methods/Design.* Here, we draw from the Global Forest Carbon Database, ForC, to provide a macroscopic overview of C cycling in the world’s forests, giving special attention to stand age-related variation. Specifically, we use `r n_records` *ForC* records for `r nrow(T1)` C cycle variables from `r n_areas_tot` geographic locations to characterize ensemble C budgets for four broad forest types -- tropical broadleaf evergreen, temperate broadleaf, temperate conifer, and taiga. We include estimates for both mature and regrowth (age <100 years) forests, and quantify trends with stand age in regrowth forests for all variables with sufficient data.

@@

```{r schematic, eval = generate_figures, echo=FALSE, fig.align = "center", fig.cap = "Figure 1 | Schematic diagram summarizing current understanding of biome differences and age trends in forest C cycling. Variables are defined in Table 1. Age trends, which represent idealized dynamics following a disturbance that removes all living vegetation, are an updated version of the classic figure from Odum (1969), with heavy lines corresponding to those in Odum's figure and $NEP$ corresponding to Odum's 'net production'. Here, $NEP$ conists primarily of woody aboveground net primary production ($ANPP_{woody}$), while $ANPP_{woody.turnover}$ is the sum of woody mortality and branch turnover. Dotted lines refer to decomposition of potential 'legacy' organic material produced prior to the disturbance and remaining at the site (e.g., standing and fallen dead wood, $DW_{tot}$; soil organic matter). Error bars on C stocks plot represent within-biome variability, wherein mean biomass is highest in the tropics, but maximum biomass is highest in temperate regions.", out.width='100%', fig.pos='H'}

@@

Data were summarized to produce schematics of C cycling for mature forets of each biome.
To obtain the values reported in the C cycle schematics, we first averaged any repeated measurements within a plot.
Values were then averaged across geographically distinct areas, defined as plots clustered within 25 km of one another [*sensu* @anderson-teixeira_forc_2018], weighting by area sampled if available for all records.
This step was taken to avoid pseudo-replication.

@@

To test for age trends in young (<100yrs) forests, we employed a mixed effects model with biome and log10[stand.age] as fixed effects and plot nested within geographic.area as a random effect on the intercept.
This analysis was run for variables with records for at least three distinct geographic areas in more than one biome, excluding any biomes that failed this criteria (Table 1). 
When the effect of stand age was significant at p $\le$ 0.05 and when each biome had records for stands of at least 10 different ages, a biome $\times$ stand.age interaction was included in the model.
We note that the logarithmic function fit in this analysis does not always correspond to theoretical expectations (Fig. `r schematic`); however, data limitations did not support fitting of functions with more parameters or reliable comparison of different functional forms.  
Within the data constraints, we deemed a logarithmic function to be the most appropriate functional form for the majority of variables.

@@

For variables with records from $\ge$ 7 distinct geographic areas, these ensemble C budgets met our criteria for budget "closure".
That is, component variables summed to within one standard deviation of their respective aggregate variables in all but one instance.
In the temperate conifer biome, the average composite measure of root biomass ($B_{root}$) was less than the combined average value of coarse and fine root biomass ($B_{root-coarse}$ and $B_{root-fine}$, respectively).
This lack of closure was driven by very high estimates of $B_{root-coarse}$ from high-biomass forests of the US Pacific Northwest.

@@

```{r eval = generate_figures, echo=FALSE, fig.align = "center", fig.cap = "Figure 7 | Age trends and biome differences in some of the major C fluxes: (a) $GPP$, (b) $NPP$, (c) $ANPP$, (d) $R_{soil}$, (e) $R_{eco}$, and (f) $NEP$. In each panel, the left scatterplot shows age trends in forests up to 100 years old, as characterized by a linear mixed effects model with fixed effects of age and biome. The fitted line indicates the effect of age on flux (solid lines: significant at p<0.05, dashed lines: non-significant), and non-parallel lines indicate a significant age x biome interaction. The boxplot illustrates distribution across mature forests, with different letters indicating significant differences between biomes. Data from biomes that did not meet the sample size criteria (see Methods) are plotted, but lack regression lines (young forests) or test of differences across biomes (mature forests). Individual figures for each flux with sufficient data, along with maps showing geographic distribution of the data, are given in the Supplement (Figs. S4-S19).", out.width='100%', fig.pos='H'}

@@

There were sufficient data to assess mature forest biome differences for nine stock variables, and significant differences among biomes were detected for five variables ($B_{tot}$, $B_{ag}$, $B_{ag-wood}$, $B_{foliage}$, $B_{root-coarse}$; Table 1).
C stocks had less consistent patterns across biomes (Figs. `r stock_age_trends`, `r all_stock_age_trends`).
For $B_{tot}$ and $B_{ag}$, tropical broadleaf forests had the highest mean biomass and boreal forests the lowest, with temperate broadleaf and needleleaf ($B_{ag}$ only) intermediate.
However, maximum values for stocks including live or standing woody biomass ($B_{tot}$, $B_{ag}$, $B_{ag-wood}$, $B_{root}$, $B_{root_coarse}$, $DW_{tot}$, $DW_{standing}$) consistently occurred in temperate biomes (Figs. `r schematic`, `r stock_age_trends`, `r all_stock_age_trends`). 
For variables that were disproportionately sampled in such high-biomass forests ($B_{ag-wood}$, $B_{foliage}$, and $B_{root-coarse}$; disproportionately sampled in  the US Pacific Northwest), temperate conifer forests had significantly higher stocks than the other biomes.

```{r eval = generate_figures, echo=FALSE, fig.align = "center", fig.cap = "Figure 8 | Age trends and biome differences in some of the major forest C stocks: (a) aboveground biomass, (b) foliage, (c) fine roots, (d) dead wood. In each panel, the left scatterplot  shows age trends in forests up to 100 years old, as characterized by a linear mixed effects model with fixed effects of age and biome. The fitted line indicates the effect of age on flux (solid lines: significant at p<0.05, dashed lines: non-significant), and non-parallel lines indicate a significant age x biome interaction. The boxplot illustrates distribution across mature forests, with different letters indicating signifant differences between biomes. Data from biomes that did not meet the sample size criteria (see Methods) are plotted, but lack regression lines (young forests) or test of differences across biomes (mature forests). Individual figures for each stock with sufficient data, along with maps showing geographic distribution of the data, are given in the Supplement (Figs. S20-S30).", out.width='100%', fig.pos='H'}

@@

*ForC* v3.0 provided unprecedented coverage of most major variables, yielding a broad picture of C cycling in the world's major forest biomes.
Carbon cycling rates generally increased from boreal to tropical regions and with stand age.
Specifically, most C fluxes were highest in tropical forests, intermediate in temperate (broadleaf or conifer) forests, and lowest in boreal forests -- a pattern that generally held for regrowth as well as mature forests (Figs. `r flux_age_trends`- `r stock_age_trends`).
The notable exception was mature forest $NEP$, which, as the difference between $GPP$ and $R_{eco}$, was indistinguishable across biomes.
There was also little directional variation in mean mature forest C stocks across biomes, although maximum values for the majority of stocks (all including live or standing woody biomass) occurred in temperate biomes (Figs. `r schematic`, `r `all_diagrams_mature`, `r stock_age_trends`).
Consistent with theory and previous studies (Fig. `r schematic`), the majority of flux variables, together with most live biomass pools, increased significantly with stand age (Table 1; Figs. `r flux_age_trends`- `r age_trends_all`, `r all_age_trends`).
Together, these results indicate that, moving from cold to tropical climates and from young to old stands, there is a general acceleration of C cycling, whereas C stocks and $NEP$ of mature forests, which are defined by the differences between in- and out- fluxes, do not vary systematically across biomes.
Together, these results refine and expand out understanding of C cycling in mature forests, while providing the first global-scale analysis of age trends in multiple forest C stocks and fluxes (Figs. `r age_trends_all`).

@@

In this analysis, the C cycle budgets for mature forests (Figs. `r all_diagrams_mature`) generally “close”–-that is, the sums of component variables do not differ from the larger fluxes by more than one standard deviation. 
On the one hand, this reflects the general fact that ecosystem-scale measurements tend to close the C budget more easily and consistently than, for example, for energy balance [@stoy_data-driven_2013]. 
On the other, however, *ForC* derives data from multiple heterogeneous sources, and standard deviations within each biome are high; as a result, the standard for C closure is relatively loose [*c.f.* @houghton_terrestrial_2020]. 
The one instance where the C budgets doesn’t close is likely due to differences in the representation of forest types (*i.e.*, disproportionate representation of US Pacific NW for  $B_{root-coarse}$ relative to  $B_{root}$; Fig. `r diagram_TeN_mature`) rather than issues of methodological accuracy. 
The overall high degree of closure implies that *ForC* gives an at least roughly consistent picture of C cycling within biomes for mature forests. 
This is an important and useful test, because it allows for consistency checks within the C cycle, for example leveraging separate and independently-measured fluxes to constrain errors in another [@phillips_value_2017; @williams_impacts_2014; @harmon_heterotrophic_2011], or producing internally consistent global data products [@wang_golum-cnp_2018].
